Using reference models in variable selection \vspace{.1in}

### 2020-04-26 paper/ref_approach.tex
fixed EbayesThresh ref
slight adjustment of fonts
more flexible float placement
fix affiliations

\usepackage{amssymb,amsmath,amsthm}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{algorithm2e}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The reference model approach in variable selection},
            pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true,
            colorlinks=true,
            linkcolor=black,
            citecolor=RoyalBlue,
            filecolor=black,
            urlcolor=RoyalBlue,
          }
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=american]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[variant=american]{english}
\fi
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{placeins}
\usepackage{graphicx,grffile,subcaption}
\textwidth 6.0 true in
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{3}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

@@

    \author{
    Federico Pavone \footnote{Department of Computer Science, Aalto University, Finland.} $\,$\footnote{Correspondence concerning this article should be addressed to Federico Pavone, Department of Decision Sciences, Bocconi University, Via R\"{o}ntgen 1, 20136 Milano, Italy. E-mail: federicopavone01@gmail.com.}, 
  Juho Piironen$^*$,
  Paul-Christian B\"{u}rkner$^*$
  and Aki Vehtari$^*$
  }

@@

The empirical Bayes median approach consists of fitting a Bayesian
model with a prior composed by a mixture of a delta spike in zero and
a heavy-tailed distribution. We use the implementation in the
\texttt{R}-package \texttt{EbayesThresh}
\citep{Silverman+etal:2017:EbayesThresh, REbayesThresh}. As suggested by
\cite{johnstone2004needles}, we use a Laplace distribution resulting
in a thresholding property, that is, there exists a threshold value
such that all the data under that threshold have posterior median
equal to zero. Therefore the selection is done by selecting only those
parameters whose posterior median is different from zero. The
hyperparameter of the Laplace distribution and the mixing weight of
the prior are estimated by marginal maximum likelihood.

>>>>

\usepackage{amssymb,amsmath,amsthm}
\usepackage{newtxtext} % times
\usepackage[scaled=.95]{cabin} % sans serif
\usepackage[varqu,varl]{inconsolata} % typewriter
\usepackage{amsmath}
\usepackage[varg]{newtxmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{algorithm2e}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The reference model approach in variable selection},
            pdfauthor={Federico Pavone, Juho Piironen, Paul-Christian B\"{u}rkner, Aki Vehtari},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true,
            colorlinks=true,
            linkcolor=black,
            citecolor=RoyalBlue,
            filecolor=black,
            urlcolor=RoyalBlue,
          }
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=american]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[variant=american]{english}
\fi
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{placeins}
\usepackage{graphicx,grffile,subcaption}
\textwidth 6.0 true in
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{3}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\renewcommand{\textfraction}{0.07}
\renewcommand{\topfraction}{0.8}
\renewcommand{\bottomfraction}{0.8}
\renewcommand{\floatpagefraction}{0.8}

@@

    \author{
      Federico Pavone\footnote{Department of Computer Science, Aalto University, Finland.}\, \footnote{Department of Decision Sciences, Bocconi University, Italy.}%$\,$\footnote{Correspondence concerning this article should be addressed to Federico Pavone, Department of Decision Sciences, Bocconi University, Via R\"{o}ntgen 1, 20136 Milano, Italy. E-mail: federicopavone01@gmail.com.}
      \,,\,
  Juho Piironen$^*$,\,
  Paul-Christian B\"{u}rkner$^*$
  and Aki Vehtari$^*$
  }

@@

The empirical Bayes median approach consists of fitting a Bayesian
model with a prior composed by a mixture of a delta spike in zero and
a heavy-tailed distribution. We use the implementation in the
\texttt{R}-package \texttt{EbayesThresh}
\citep{Silverman+etal:2017:EbayesThresh}. As suggested by
\cite{johnstone2004needles}, we use a Laplace distribution resulting
in a thresholding property, that is, there exists a threshold value
such that all the data under that threshold have posterior median
equal to zero. Therefore the selection is done by selecting only those
parameters whose posterior median is different from zero. The
hyperparameter of the Laplace distribution and the mixing weight of
the prior are estimated by marginal maximum likelihood.
